Titeltext

### 2018-07-25 thesis/paper/paper.tex
Added property scope

Additional predicates modelling different preprocessing steps are explained in chapter \ref{cha_rules}.
\section{Terminology}
\begin{table}[H]
\caption{shorthands}
\begin{tabular}{ll}
Shorthand & Description \\
\hline
constrained statement & statement with the constrained property as predicate \\
item statement & statement on the same item as the constrained statement \\
constrained item & item with a constrained statement
\end{tabular}
\end{table}
\chapter{Property Constraints}

@@

>>>>

Additional predicates modelling different preprocessing steps are explained in chapter \ref{cha_rules}.
\section{Terminology}
\begin{table}[H]
\caption{shorthands}
\begin{tabular}{ll}
Shorthand & Description \\
\hline
constrained statement & statement with the constrained property as predicate \\
constrained qualifier & qualifier with the constrained property as predicate \\
constrained reference & reference with the constrained property as predicate \\
constrained item & item with a constrained statement \\
item statement & statement on the same item as the constrained statement \\
\end{tabular}
\end{table}
\chapter{Property Constraints}

@@

\subsection{Property scope (Q53869507)}
The property scope constraint specifies if a property may be used in a statement, qualifier or reference as predicate.
\begin{table}[H]
\caption{property scope constraint (Q53869507)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & constrained statement \\
\hline
Qualifiers & \makecell{property scope (P5314) -- 1..3 \\ must be as main value (Q54828448), as qualifier (Q54828449) or as reference (Q54828450) \\ specifies allowed use in statements, qualifiers or references} \\
\hline
Violation & constrained statement in a position that is not allowed \\
\hline
Dependency & constrained statement, qualifier or reference \\
\hline
\end{tabularx}
\end{table}

Since only three posibilities exist, this is equivalent to forbidding all other possibilities and the rules are simple mapping all of tripleEDB, qualifierEDB and referenceEDB with the constrained property that are not allowed.
